---
title: "Spring 2020 Research Report"
author: "mawaskow"
date: "5/12/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### VIP Lab
Aside from my work in the USGS river digitizing project, this semester I have been doing work in the VIPLab concerning the problem of determining the ideal drone height over data collection sites.

This problem, and the research project design in order to solve it, require a myriad of background information.

Given a selection of data recorded in the past, I generated DSMs, DTMs, CHMs, and orthophotos from various softwares and have compiled them in this report so that their outputs and quality can be compared.


### Initial Data
The data recorded in the past was:
```{r echo= FALSE, results = 'asis'}
table1 <- read.csv("quasimetadata.csv", header = TRUE, sep = ",")
library(knitr)
kable(table1)
```


### Code
Below is the R code which takes the path of a folder containing DSMs and DTMs (if the files are labelled appropriately), and outputs to that same file CHMs with names corresponding to the names of their respective DSMs and DTMs:

```
library(raster)
library(rgdal)
###

generate_chm <- function(dtmfilename, dsmfilename, chmoutfilename){
  dtm_raster <- raster(dtmfilename)
  dsm_raster <- raster(dsmfilename)
  chm_raster <- dsm_raster - dtm_raster
  plot(chm_raster, 1000000, 1000000, main = chmoutfilename)
  writeRaster(chm_raster, chmoutfilename,
              format= "GTiff", overwrite = TRUE)
}

dsmfiles <- c(list.files("Data", pattern = "*DSM.tif", full.names = 'True'))
dtmfiles <- c(list.files("Data", pattern = "*DTM.tif", full.names = 'True'))

for (i in seq_along(dsmfiles)){
  len = nchar(dsmfiles[i])
  begin = substr(dsmfiles[i], 1, len-7)
  end = "CHM.tif"
  chmname = paste(begin, end, sep = "")
  generate_chm(dtmfiles[i], dsmfiles[i], chmname)
}
```

What follows is the R code which takes the path of a folder containing orthophotos and (if the files are labeled correctly) outputs an NDVI to the same folder with a name corresponding to the name of the orthophoto file.
```
library(raster)
library(rgdal)
library(rgeos)
library(RColorBrewer)

##### function #####
generate_ndvi <- function(orthophotoinfile, ndvioutfile){
  options(stringsAsFactors = FALSE)
  orthoforndvi <- stack(orthophotoinfile)
  orthoforndvi_brick <- brick(orthoforndvi)
  r_brick <- orthoforndvi_brick[[1]]
  nir_brick <- orthoforndvi_brick[[4]]
  ndvicalc <- (nir_brick - r_brick) / (nir_brick + r_brick)
  writeRaster(x = ndvicalc,
              filename= ndvioutfile, format = "GTiff", datatype='INT2S', overwrite = TRUE)
}

##### Here (the "Data" entry) is where you select the folder path from which you will select the files #####
filenames <- c(list.files("Data", pattern = "*orthophoto.tif", full.names = 'True'))

##### main code #####
for (i in seq_along(filenames)){
  len = nchar(filenames[i])
  begin = substr(filenames[i], 1, len-14)
  end = "NDVI.tif"
  ndviname = paste(begin, end, sep = "")
  generate_ndvi(filenames[i], ndviname)
}
```

### Program Outputs

#### WebODM
### DSMs and DTMs

![Santa Rita DSM](Data/WebODM/basefiles/SantaRitaDSM.tif) ![Santa Rita DTM](Data/WebODM/basefiles/SantaRitaDTM.tif)

![Santa Rita Project 1 DSM](Data/WebODM/basefiles/SantaRitaProj1DSM.tif) ![Santa Rita Project 1 DTM](Data/WebODM/basefiles/SantaRitaProj1DTM.tif)

![Santa Rita Project 3 DSM](Data/WebODM/basefiles/SantaRitaProj3DSM.tif) ![Santa Rita Project 3 DTM](Data/WebODM/basefiles/SantaRitaProj3DTM.tif)

![Santa Rita Project 5 DSM](Data/WebODM/basefiles/SantaRitaProj5DSM.tif) ![Santa Rita Project 5 DTM](Data/WebODM/basefiles/SantaRitaProj5DTM.tif)

### CHMs

![Santa Rita CHM](Data/WebODM/generated/SantaRitaCHM.tif) ![Santa Rita Project 1 CHM](Data/WebODM/generated/SantaRitaProj1CHM.tif)

### Orthophotos

![Santa Rita Orthophoto](Data/WebODM/generated/SantaRitaorthophoto.tif) ![Santa Rita Project 1 Orthophoto](Data/WebODM/generated/SantaRitaProj1orthophoto.tif)

### NDVIs

![Santa Rita NDVI](Data/WebODM/generated/SantaRitaNDVI.tif) ![Santa Rita Project 1 NDVI](Data/WebODM/generated/SantaRitaProj1NDVI.tif)